Job Demands-Resources model components through the lens of O*NET classifications

### 2023-02-07 Submission.Rmd
Reviewed and edited up to the discussion section. We need to find the table of SDs and link to it as we indicate in the results section. The Excel table of items should also be referenced probably in the materials section.

---
title             : "Job Demands-Resources model components through the lens of O*NET classifications"
shorttitle        : "O*NET JD-R"

@@

abstract: |
  O\*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource. All the results of this current study match the stress-appraisal stuff. Next steps: 1) discuss results within stress-appraisal framework [@lazarus1984stress], 2) different literature on challenge and hindrance demands. Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings. JDR neglects the other 2 literatures. Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those. Maybe forget about cross-walk thing. May actually want to start with this: https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit#gid=1041061499.[^foot1]

  We want to also group items by O\*NET categories so there's not so many (that makes ANOVAs more viable)

@@

Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlight the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance. However, much of our existing knowledge of the way this model functions is grounded in the assumption that characteristics are generally considered resources or generally considered demands. We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges]. We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, which a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

@@

The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model [@demerouti2001job]. One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [e.g., high work pressure is frequently cited as a common demand; @demerouti2001job]. Cognitively, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) [@bakker2014job]. Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience depsite the typical apriori assignment of a characteristic as objectively a "demand" or "resource". We explore this further below.

@@

As described in the last paragraph, job context and characteristics are assigned or appraised as demands or resources. Although much of our research on job demands in particular is based on apriori classifications of demands [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand. The stress process speaks to how such individual difference in appraisal is possible. @lazarus1984stress presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis. Via this process, meaning is assigned to stimuli based on potential for gain or loss. If appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping. The cycle of appraisal then continues based on the action to cope with the stressor [@lazarus1984stress]. Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor should an event or situation be deemed so. Although not suggested by the names, primary and secondary appraisals can happen simultaneously. For instance, available resources to cope with a stressor may influence an employee’s initial appraisal of a stressor (e.g., amount of time [resource] available to prepare for the speech may influence one’s primary appraisal of this ask).

@@

Although there is a tendency to attach a negative connotation to the word “stress”, @selye1936syndrome defined stress as a response to change, which is quite non-specific. We return to the employed public figure for this next section. It is quite probable that two employees would be called upon to serve as a spokesperson for their organization in a time of need. One may appraise the circumstance as an opportunity to positively influence others, while the other may plausibly feel paralyzed by the task. In fact, @bakker2017job call attention to different types of demands in their recent review of, and future directions, for work on the job-demands resources theory.

@@

Prior to considering the subsequent empirical work done on this topic, it is of value to explore *why* there is expected to be different outcomes associated with these forms of demands. @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes. Similar to the job-demands resources theory [@bakker2017job], challenge and hindrance demands elicit two different paths or processes. First, challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. The other side of the coin is that this energy may be depleted eventually, leading to strain. Hindrance stressors elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge].

We next consider the empirical evidence on this topic. The broadest, and perhaps first question, we should ask is whether people perceive demands as challenges vs. hindrances, or whether all demands are under a larger “demands” category. Evidence suggests the employees do, in fact, distinguish between challenge and hindrance stressors [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending]. For example, @bakker2013weekly found that perceived work pressure as a hindrance demand, and emotional demands as more of a challenge demand. @webster2011extending approached this question with three common workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees. @kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing. The opposite occurred when a demand was appraised as a hindrance – in those instances, the appraisal had a negative association with motivational resources.

Having evidence that people can make a distinction between challenge and hindrance stressors, the next logical question is whether they do relate differentially to outcomes. The challenge-hindrance stressor framework has, in fact, been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing. A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic. For example, @cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. @chen2021daily found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment. Daily hindrance demands were negatively related to these outcomes. In contrast, @abbas2019challenge found that challenge and hindrance stressors were *both* positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it [@crawford2010linking]. Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety [@rodell2009can]. Lastly, @gerich2017relevance concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.

We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point, and a rich collection of them support differential associations across a variety of organizational outcomes. For example, both challenges and hindrances have been shown to positively predict strain [@lepine2005meta; @podsakoff2007differential; @webster2010toward]. Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction. For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressor [@lepine2005meta]. Turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors [@podsakoff2007differential]. @kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals.

@horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching JD-R model. In fact, @horan2020review state that “…stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p. 3). In fact, @horan2020review suggest future research continue to move away from apriori classifications of stressors, as doing so can be problematic for theoretical and empirical reasons. Theoretically, apriori classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time [e.g., @searle2015merits].

## O\*Net Resource

Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would “…promote the effective education, training, counseling, and employment of the American workforce. It should accomplish its purpose by providing a database system that identifies, defines, classifies, and describes occupations in the economy in an accessible and flexible manner” [@advisory1993new, p. 6]. The result was the now commonly used O\*NET. The Occupational Information Network (O\*NET; onetonline.org) contains a comprehensive description of occupations [@peterson2001understanding]. This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated. In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the [Industrial and Organizational Psychologist listing on O\*Net](https://www.onetonline.org/link/summary/19-3032.00). These data, and the tools provided for free on the website (e.g., Career Exploration Tools, “My Next Move for Veterans”, “My Next Move”, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice. It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.

@@

Of greatest interest here are statements taken from O\*NET ["activity" and "context" classifications](https://www.O\*NETonline.org/find/descriptor/result/4.A.1.b.3) (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics). One of the first and basic questions is whether or not the categorical examples of "resources" and "demands" described in the Job Demands-Resources Theory [@demerouti2001job], for example, are generally deemed resources or demands as we objectively define them. The next logical question surrounds how "universal" such ratings are. For instance, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.

@@

Lastly, we propose three research questions that explicitly address a topic discussed above. Although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, there remains variability in these appraisals [@lepine2022challenge]. @lepine2022challenge, in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal. We explore whether literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job] and challenge-hindrance stressor framework [@cavanaugh2000empirical].

@@

We used 98 statements taken from O\*NET [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3). We retained 41 work activity classifications which O\*NET groups into categories of information input (5 statements; Where and how are the information and data gained that are needed to perform this job?), interacting with others (17 statements; What interactions with other persons or supervisory activities occur while performing this job?), mental processes (10 statements; What processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (9 statements; What physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Fifty-seven work context statements grouped into interpersonal relationships (14 statements; This category describes the context of the job in terms of human interaction processes), physical work conditions (30 statements; This category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (13 statements; This category involves the relationships or interactions between the worker and the structural characteristics of the job).

@@

## Standard deviations of perceptions

@@

The first prediction asks whether job characteristics differ in variability/stability regarding
subjective worker perception as a demand or resource. Figure \@ref(fig:overallhist) presents standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand. As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's $K^2$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).

## Low Variability Demands and Resources

@@

## High Variability Demands and Resources

@@

## Correlations

Table \@ref(tab:cortab) highlights hypothesis 2. A large number of correlations are moderate. Challenge and hindrance demands are smaller in relationship but mostly negative. Challenge and resource are typically large. Only some are small (for example information input and physical challenges). For the most part there are strong associations between challenges and resources.

@@

Figure 4 highs the average characteristic rating grouped by the literature implicated categories shown on the right. These categories are frequently presented in descriptions of the JD-R model and theory (cite). To answer these research questions, authors categorized items into the categories listed in the literature. For example, autonomy is frequently described as a resource. An O*Net item in the “autonomy” category is “How much decision making freedom, without supervision, does your job offer?”. Means for respondent-rated resources, challenges, and hindrances were then computed to explore whether literature-implicated resources and demands were consistently rated as such. The left side of Figure 8 shows literature-derived demands (e.g., work pressure). We do not see a clear pattern of high ratings as hindrances for these demands. In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much more variability in how employees rated what should objectively be "hindrances" at work. However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings. Here, the white bars representing resources are consistently higher. ADD ANOVAS HERE - one way repeated measures for each category (total of 10 analyses). describe pattern. In sum, these results provide ___ support for RQ 1 and 2.

challenges

>>>>

---
title             : "Job Demands-Resources Model Components through the Lens of O*NET Classifications"
shorttitle        : "O*NET JD-R"

@@

abstract: |
  We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. O*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource.

@@

Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance among other outcomes. However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that job characteristics are generally considered resources or generally considered demands. We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges]. We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resources) in the workplace, with a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

@@

The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model [@demerouti2001job]. One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [e.g., high work pressure is frequently cited as a common demand; @demerouti2001job]. Cognitively, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) [@bakker2014job]. Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical apriori assignment of a characteristic as objectively a "demand" or "resource". We explore this further below.

@@

As described in the last paragraph, job context and characteristics are assigned or appraised as demands or resources. Although much of our research on job demands in particular is based on apriori classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand. The stress process speaks to how such individual difference in appraisal is possible. @lazarus1984stress presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis. Via this process, meaning is assigned to stimuli based on potential for gain or loss. If appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping. The cycle of appraisal then continues based on the action to cope with the stressor [@lazarus1984stress]. Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor. Although not suggested by the names, primary and secondary appraisals can happen simultaneously. For instance, available resources to cope with a stressor may influence an employee’s initial appraisal of a stressor (e.g., amount of time [resource] available to prepare for the speech may influence one’s primary appraisal of this ask).

@@

Although there is a tendency to attach a negative connotation to the word “stress”, @selye1936syndrome defined stress as simple a response to change. We return to the employed public figure for this next section. Consider two employees be called upon to serve as spokespeople for their organization. One may appraise the circumstance as an opportunity to positively influence others, while the other may feel daunted by the task.

@@

Prior to considering the subsequent empirical work on this topic, it is of value to explore *why* different outcomes are expected with these forms of demands. @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes. Similar to the job-demands resources theory [@bakker2017job], challenge and hindrance demands elicit two different paths or processes. First, challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. Hindrance stressors elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge].

We next consider the empirical evidence on this topic. The first question we should ask is whether people distinguish between challenge vs. hindrance demands, or whether all demands are under a larger “demands” category. Evidence suggests the employees do, in fact, differentiate between challenge and hindrance stressors [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending]. For example, @bakker2013weekly found that work pressure was perceived as a hindrance demand, and emotional demands as more of a challenge demand. @webster2011extending approached this question with three common workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hindrance demands to different degrees.

Appraisals are associated with different forms of coping, and subsequently, outcomes. The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing. A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic. @kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing. The opposite occurred when a demand was appraised as a hindrance – in those instances, the appraisal had a negative association with motivational resources. @cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. @chen2021daily found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment. Daily hindrance demands were negatively related to these outcomes. In contrast, @abbas2019challenge found that challenge and hindrance stressors were *both* positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it [@crawford2010linking]. Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety [@rodell2009can]. Lastly, @gerich2017relevance concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.

We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point, and a rich collection of them support differential associations across a variety of organizational outcomes as well. For example, both challenges and hindrances have been shown to positively predict strain [@lepine2005meta; @podsakoff2007differential; @webster2010toward]. Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction. For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressor [@lepine2005meta]. Turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors [@podsakoff2007differential]. @kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals.

@horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching JD-R model. In fact, @horan2020review state that “…stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p. 3). In fact, @horan2020review suggest future research continue to move away from apriori classifications of stressors, as doing so can be problematic for theoretical and empirical reasons. Theoretically, apriori classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time [e.g., @searle2015merits]. TRANSITION NEEDED HERE. I DELETED THE ONET PARAGRAPH.

@@

The integration of the literature above results in two primary predictions. The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands. For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals [@lepine2022challenge]. @lepine2022challenge, in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal. Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.

@@

We explore three research questions addressing whether our literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job] and challenge-hindrance stressor framework [@cavanaugh2000empirical].

@@

The Occupational Information Network (O\*NET; onetonline.org) contains a comprehensive description of occupations [@peterson2001understanding]. This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated. We used 98 statements taken from O\*NET [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3). We retained 41 work activity classifications which O\*NET groups into categories of information input (5 statements; Where and how are the information and data gained that are needed to perform this job?), interacting with others (17 statements; What interactions with other persons or supervisory activities occur while performing this job?), mental processes (10 statements; What processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (9 statements; What physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Fifty-seven work context statements grouped into interpersonal relationships (14 statements; This category describes the context of the job in terms of human interaction processes), physical work conditions (30 statements; This category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (13 statements; This category involves the relationships or interactions between the worker and the structural characteristics of the job).

@@

@@

The first prediction asks whether job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource. Figure \@ref(fig:overallhist) presents frequency distributions standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand. As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's $K^2$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).

@@

@@

The second prediction stated that job characteristics would not be uniquely categorized as a resource or demand. Table \@ref(tab:cortab) provides the correlations among the O\*Net item groupings by resource, challenge and hindrance demand. A large proportion of correlations are moderate. Challenge and hindrance demands are smaller in relationship, but mostly negative. Challenge and resource are strongly and positively related. These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics. Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.

@@

In addition to the two predictions, three related research questions were proposed. To answer these research questions, authors first categorized items into the categories listed in the JD-R literature. For example, autonomy is frequently described as a resource. An O\*Net item in the autonomy category is, “How much decision making freedom, without supervision, does your job offer?”. Means for resources, challenges, and hindrances groupings were then computed to explore whether literature-implicated resources and demands were consistently rated as such. The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure). Here, we do not see a clear pattern of high ratings as hindrances for these demands. In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much more variability in how employees rated what should objectively be "hindrances" at work. However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings. The white bars representing resources are consistently higher. ADD ANOVAS HERE - one way repeated measures for each category (total of 10 analyses). describe pattern. In sum, these results provide ___ support for RQ 1 and 2.
